Water Management

### 2020-02-24 Paper/paper.tex
unify headings

\subsubsection{Modification 2: Increased Rainfall Volatility}
To consider the predicted impacts of climate change \citep{guhathakurta2011impact}, we look at the effect of increased rainfall volatility. 
We do this by using a  $\sigma^2$ of x. % TODO: Das ist noch nicht ganz richtig

@@

\subsection{Evaporation}
In the following, we want to assess the effect of evaporation on the optimal irrigation policy and the steady state. 
As described in \ref{sec:intro-mod4}, we derive the amount of evaporation over time from other weather related and geographical data. 
The (calculated) evaporation has a low volatility over the years and has value of approximately 1 unit, as \ref{fig:without-vs-with-evaporation} shows. 
Due to the fact that the reservoir has a fixed capacity of 7 units, rainfall that would fill the reservoir above this value is not available for further use. 
When taking evaporation into account, the reservoir never reaches its capacity limits and thus all rainfall will be saved. This leads to an increased volatility of the water level. 
\\

>>>>

\subsubsection{Modification 2: Increased Volatility of Rainfalls}
To consider the predicted impacts of climate change \citep{guhathakurta2011impact}, we look at the effect of increased rainfall volatility. 
We do this by using a  $\sigma^2$ of x. % TODO: Das ist noch nicht ganz richtig

@@

\subsection{Taking Evaporation Into Account}
In the following, we want to assess the effect of evaporation on the optimal irrigation policy and the steady state. 
As described in \ref{sec:intro-mod4}, we derive the amount of evaporation over time from other weather related and geographical data. 
The (calculated) evaporation has a low volatility over the years and has value of approximately 1 unit, as \ref{fig:without-vs-with-evaporation} shows. 
Due to the fact that the reservoir has a fixed capacity of 7 units, rainfall that would fill the reservoir above this value is not available for further use. 
When taking evaporation into account, the reservoir never reaches its capacity limits and thus all rainfall will be saved. This leads to an increased volatility of the water level. 
\\
